\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.0cm,right=1.06cm,bottom=0.49cm]{geometry}


%by: Aline R. Antunes

\begin{document}
\begin{center}
    \Large \textbf{Luiz Augusto Fidalgo}\\
    \hrulefill
\end{center}

\begin{center}
    Frankfurt, Germany \textbullet \ \href{http://luizfidalgo.com}{luizfidalgo.com} \\
    \href{mailto:luiz.fidalgo@hotmail.com}{luiz.fidalgo@hotmail.com} \textbullet \ \href{https://github.com/lafidalgo}{github.com/lafidalgo} \textbullet \ \href{https://linkedin.com/in/luiz-fidalgo/}{linkedin.com/in/luiz-fidalgo/}
\end{center}

%\vspace{0.5pt}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{University of Brasília} \hfill Brasília, Brazil

Bachelor of Electrical Engineering \hfill Mar 2018 - Feb 2024

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    %\item Recognized as one of Brazil's top universities.
    \item Graduated with honors as the Outstanding Student of my class.
\end{itemize}

\vspace{12pt}

\textbf{University of Rome Tor Vergata} \hfill Rome, Italy

International Sandwich Program \hfill    Feb 2023 - Aug 2023

\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Attended master's level courses into Artificial Intelligence, IoT and VLSI.
\end{itemize}

%\vspace{12pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Hotmart} \hfill Amsterdam, Netherlands (Remote)

\textbf{Machine Learning Engineer} \hfill Aug 2024 – Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Assisted Data Scientists in deploying machine learning models into production using SageMaker and EKS.
    \item Developed high-performance APIs for AI applications using LLMs, RAG, and AI agents, optimizing integration and scalability for developers and clients.
    \item Created automation tools to streamline CI/CD pipelines, utilizing Docker, Kubernetes, and Terraform, significantly improving deployment efficiency and reducing release times.
    \item Authored RFCs and documentation to standardize workflows and ensure effective project execution.
\end{itemize}

\vspace{12pt}

\textbf{SnowFox AI} \hfill Brasília, Brazil (Remote)

\textbf{Machine Learning Engineer} \hfill Sep 2023 – Aug 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed a pipeline to extract information from unstructured documents using OCR, LLMs, and RAG. Achieved human-comparable results with significantly faster processing times.
    \item Developed and deployed a computer vision solution for high-cardinality object detection and classification, including model training and scalable infrastructure setup using Kubernetes and Docker.
    \item Integrated state-of-the-art technologies like GPT-4o, SAM, YOLOv8, and other Foundation Models to enhance AI system performance in real-world applications.
    \item Architected and implemented cloud infrastructure for MLOps across GCP, AWS, and Azure environments;
\end{itemize}

\vspace{12pt}

\textbf{GrupoOrion} \hfill Brasília, Brazil

\textbf{Hardware and Software Development Intern} \hfill Mar 2021 – Dec 2022
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Contributed to the development of 5 IoT sensor prototypes and supported the production, testing, and installation of over 200 units.
    \item Worked with microcontrollers and microprocessors to develop and optimize hardware solutions.
    \item Recognized as the company's Outstanding Intern of 2021.
\end{itemize}

\begin{center}
    \textbf{Technologies \& Skills}
\end{center}

\textbf{Programming Languages:} Python, C, C++

\textbf{AI \& ML:} Pandas, Numpy, scikit-learn, TensorFlow, PyTorch, MLflow

\textbf{LLM, RAG \& AI Agents Frameworks:}  LangChain, LLamaIndex, CrewAi

\textbf{AWS:} S3, Lambda, ECR, EKS, SageMaker, Textract, DynamoDB, SQS

\textbf{GCP:} Cloud Storage, Cloud Functions, Cloud Run, Vertex AI, AutoML, GKE

\textbf{DevOps:} Docker, Terraform, Kubernetes, CI/CD, GitHub Actions

\textbf{Web Frameworks:} FastAPI, Flask, Streamlit

\textbf{Data Visualization:} Matplotlib, Plotly

\textbf{Soft Skills:} Leadership, Communication, Cross-functional Teamwork, Problem-Solving, Critical Thinking

\textbf{Languages:} English (C2), German (A2), Portuguese (Native)

\end{document}
